Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-06 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
testing new git password so I added minor text edit.
Updated smoke map.

##2. Wildfire smoke descriptive characteristics
Map of smoke count and smoke time series will go here.

>>>>

##2. Wildfire smoke descriptive characteristics

Importing ZIP code-level population-weighted PM~2.5~ daily data.

```{r smoke data import and wrangle}
# pm path
pm_path <- paste0("./data/pm/2013-oregon_county_pm25.csv")
# county pm
county_pm_df <- read_csv(pm_path)

# estimate county smoke 
county_smk_count <- county_pm_df %>% 
  # binary smoke variable at >10 ug/m^3
  mutate(gwr_smk10 = ifelse(geo_smk_pm >= 10, 1, 0)) %>% 
  group_by(county) %>% 
  summarise(smk_day10 = sum(gwr_smk10)) %>% 
  # lower case county name and remove "." to match spatial df
  mutate(subregion = tolower(stringr::str_replace(county, "[.]", " ")))

# use the map function from the maps package to get the polygon data
county_poly <- maps:::map("county", "oregon", plot=FALSE, fill = TRUE)
# find centroids
county_centroids <- maps:::apply.polygon(county_poly, maps:::centroid.polygon)

# create a data frame for graphing out of the centroids of each polygon
county_centroids <- county_centroids[!is.na(names(county_centroids))]
centroid_array <- Rreduce(rbind, county_centroids)

dimnames(centroid_array) <- list(gsub("[^,]*,", "", names(county_centroids)),
                                 c("long", "lat"))
county_text <- as.data.frame(centroid_array)
county_text$county <- rownames(label_df)
```

### Number of days in Oregon where smoke PM~2.5~ exceeded 10 ug/m^3.

```{r smoke days map}

smoke_map <- ggplot(or_county_spatial_df, aes(x=long,y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill =smk_day10)) +
  scale_fill_gradient(expression("Smoke Days > 10 µg/m"^3),
    low= "#3B9AB2", high="#F21A00", 
    guide = guide_colorbar(direction="horizontal", title.position = "top",
                           title.hjust = 0.5, barwidth = 20)) +
  # add county path on top
  geom_path(colour="#EBCC2A") +
  # add county text 
  geom_text(data = county_text, aes(x=long, y=lat, label = county, group=NULL), 
    colour = "white", size = 2.5) +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.text = element_text(size = 13),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA),
    legend.position = "bottom")

smoke_map
```

Most of the heavy smoke days were in the south-west part of Oregon. I've added county names to map but some text aren't well placed. I should probably use centroid, but then I'll have to import a shapefile to do this. I'll fix this later; I plan to add in fire locations.

### Time-series of geo-weighted regression estimates of smoke PM~2.5~ by county
